Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
Simplified motivation section, removed Fig2

We identified a hierarchy of constructs pertaining to the motivation people have for using social
machines with top level constructs of:

\begin{enumerate}
\item Hedonistic
\item Financial
\item To be informed
\item To help others
\end{enumerate}

The sub constructs are illustrated in Figure~\ref{motivation}, and we relate them to Maslow's hierarchy of needs~\cite{maslow}, (e.g., self-actualisation, security, respect of others), in various ways.

\begin{figure*}[htb]
\begin{center}
\includegraphics[width=18cm]{img/motivation.pdf}
\caption{Motivation hierarchy of participants using Social Machines, related to Maslow's hierarchy of needs.} \label{motivation}
\end{center}
\end{figure*}

For each of these motivations, different roles that participate may have different {\it core motivations}, such as:

>>>>

%We identified a hierarchy of constructs pertaining to the motivation people have for using social
%machines with top level constructs of:
%
%\begin{enumerate}
%\item Hedonistic
%\item Financial
%\item To be informed
%\item To help others
%\end{enumerate}
%
%The sub constructs are illustrated in Figure~\ref{motivation}, and we relate them to Maslow's hierarchy of needs~\cite{maslow}, (e.g., self-actualisation, security, respect of others), in various ways.
%
%\begin{figure*}[htb]
%\begin{center}
%\includegraphics[width=18cm]{img/motivation.pdf}
%\caption{Motivation hierarchy of participants using Social Machines, related to Maslow's hierarchy of needs.} \label{motivation}
%\end{center}
%\end{figure*}

The motivations of users can be identified and mapped to existing human needs and motivations
systems, such as Maslow's hierarchy of human needs~\cite{maslow} (e.g., self-actualisation, security
respect of others). For each of these motivations, different roles that participate may have different {\it core motivations}, such as:
